Empirical Bayes estimation of the normal inverse Gaussian prior in simultaneous-equation models

### 2019-08-15 docs/manuscript1.Rnw
added unpenalized covariates and intercept (not tested)

	We are not the first to propose to learn from external data 
	across equations and features. \cite{kpogbezan_incorporating_2019} uses 
	the presence or absence of edges in a normal tissue apoptosis pathway, to aid 
	in the estimation of a cancer tissue apoptosis pathway. Furhtermore, in an 
	eQTLs detection problem they include the location of the SNPs (inside
	the gene or not) to aid in the estimation. \cite{oman_minimax_2002} uses 
	empirical Bayes to learn from external data concerning both the outcomes and 
	the features in a low dimensional chemometrics dataset. Our proposed method,
	termed [! acronym here],
	extends \cite{kpogbezan_incorporating_2019,kpogbezan_empirical_2017} by 
	allowing for the inclusion of continuous external information and several 
	sources of information.

	- think of acronym

>>>>

	We are not the first to propose to learn from external data 
	across equations and features. \cite{kpogbezan_incorporating_2019} uses 
	the presence or absence of edges in a normal tissue apoptosis pathway, to aid 
	in the estimation of a cancer tissue apoptosis pathway. Furhtermore, in an 
	eQTLs detection problem they include the location of the SNPs (inside
	the gene or not) to aid in the estimation. \cite{oman_minimax_2002} uses 
	empirical Bayes to learn from external data concerning both the outcomes and 
	the features in a low dimensional chemometrics dataset. Our proposed method,
	termed \texttt{semnig},
	extends \cite{kpogbezan_incorporating_2019,kpogbezan_empirical_2017} by 
	allowing for the inclusion of continuous external information and several 
	sources of information.
